GPU-Beschleunigung der Material Point Method

### 2018-11-25 mscthesis.tex
conj. gradients, midpoint

  \item $C^1$-continuity s.t. $\nabla w_i$ is continuous.

@@

  = \sum_p V^0_p P_{\alpha\beta}(\hat{\boldsymbol{F}}_{Ep})F_{\gamma\beta}\frac{\partial w_{ip}}{\partial x_\gamma} = -\hat{f}_{i\alpha}

@@

where the force can be also described in terms of the Cauchy stress:

@@

Due to eq. \ref{eq:def_grad_lambda} we can for the class of functions summarize the stress computation as:

@@

@@

@@

@@

@@

  \caption{Euclid’s algorithm}\label{euclid}

@@

    \Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
    \State $r\gets a\boldsymbolod b$ and \var{foobar}\label{foobar}
    \While{$r\not=0$}\Comment{We have the answer if r is 0}
    \State $a\gets b$
    \State $b\gets r$
    \State $r\gets a\boldsymbolod b$
    \EndWhile\label{euclidendwhile}
    \State \textbf{return} $b$\Comment{The gcd is b}

@@

Sparse: \cite{OPENVDB} \cite{NVIDIA:GVDB_VOXELS}
\begin{appendices}
  \section{"Inertia Tensor" for Cubic Splines}\label{app:dp_proof}
  \begin{code}
\caption{$\boldsymbol{D}_p$ proof}
  \begin{minted}{python}
import numpy as np
from sympy import *

>>>>

  \item $C^1$-continuity s.t. $\nabla w$ is continuous.

@@

  = \sum_p V^0_p P_{\alpha\beta}(\hat{\boldsymbol{F}}_{Ep})F_{\gamma\beta}\frac{\partial w_{ip}}{\partial x_\gamma} = -\hat{f}_{i\alpha}.

@@

The nodal force can be also described in terms of the Cauchy stress:

@@

Due to eq. \ref{eq:def_grad_lambda} the stress computation is summarized for the class of functions in use as:

@@

\begin{equation}\label{eq:vel_midpoint}

@@

\begin{equation}\label{eq:force_midpoint}

@@

The modified energy conserving implicit midpoint scheme from \cite{GONZALEZ} for the Material Point Method differs from this by the use of a trapezoidal approximation of $\boldsymbol{v}_i^{n+\frac{1}{2}}$:
\begin{equation}\label{eq:trapezoidal}
  \boldsymbol{v}_i^{n+\frac{1}{2}} \approx \frac{\boldsymbol{\hat{v}}_i^{n+1} + \boldsymbol{v}_i^{n}}{2}.
The trapezoidal rule has the same order of error $O(\Delta t^2)$ as the implicit midpoint scheme. This modification allows for a more direct one-step scheme as shown in the following. Plugging in eq. \ref{eq:vel_midpoint} into \ref{eq:force_midpoint}:

@@

  m_i^n \frac{\boldsymbol{\hat{v}}^{n+1}-\boldsymbol{v}_i^n}{\Delta t} = \boldsymbol{f}_i \left( \frac{\boldsymbol{x_i}^n+\boldsymbol{x_i}^n + \Delta t \left( \frac{\boldsymbol{\hat{v}}_i^{n+1} + \boldsymbol{v}_i^{n}}{2}
\right)
    }{2}\right)

@@

  \caption{Conjugate gradient}\label{alg:conj_grad}

@@

    \Procedure{CONJUGATE-GRADIENT}{$A,x,b$}
    \State $\boldsymbol{r}\gets \boldsymbol{b} - \boldsymbol{Ax}$
    \State $\boldsymbol{p}\gets \boldsymbol{r}$
    \State $\gamma \gets \langle \boldsymbol { r } , \boldsymbol { r } \rangle$
    \Repeat
      \State $\boldsymbol { s } \gets \boldsymbol { A } \boldsymbol { p }$
      \State $\alpha \gets \frac { \gamma } { \langle \boldsymbol { p } , \boldsymbol { s } \rangle }$
      \State $\boldsymbol { x } \gets \boldsymbol { x } + \alpha \boldsymbol { p }$
      \State $\boldsymbol { r } \leftarrow \boldsymbol { r } - \alpha \boldsymbol { s }$
      \State $\kappa \leftarrow \langle \boldsymbol { r } , \boldsymbol { r } \rangle$
      \If{$ \kappa < \epsilon$} \Comment{alt. fixed amount of steps}
        \State \Return \label{alg:conj_grad:exit}
      \EndIf
      \State $\beta \gets \frac{\kappa}{\gamma}$
      \State $\boldsymbol { p } \leftarrow \boldsymbol { r } + \beta \boldsymbol { p }$
      \State $\gamma \gets \kappa$
      \Until{false} \Comment{exit at \ref{alg:conj_grad:exit}}

@@

Sparse: \cite{OPENVDB} \cite{NVIDIA:GVDB_VOXELS}
\clearpage
\begin{appendices}
  \section{"Inertia Tensor" for Cubic Splines}\label{app:dp_proof}
  \begin{code}
\caption{$\boldsymbol{D}_p$ proof}
  \begin{minted}{python}
import numpy as np
from sympy import *
